---
output:
  # bookdown::pdf_document2:
  #   keep_tex: true
  #   toc: false
  bookdown::word_document2:
    toc: false
geometry: margin=1.0in
font-size: 12pt
header-includes:
  - \usepackage{helvet}
  - \renewcommand*\familydefault{\sfdefault}
  - \usepackage{setspace}
  - \doublespacing
  - \usepackage[left]{lineno}
  - \linenumbers
bibliography: references.bib
csl: https://www.zotero.org/styles/estuarine-coastal-and-shelf-science
---
```{r, include=FALSE, message=FALSE}
library(targets)
options(knitr.kable.NA = '')
options(tinytex.verbose = TRUE)
# knitr::opts_knit$set(root.dir = dirname(here::here()))
```

```{r, include=FALSE, message=FALSE}
today <- Sys.Date()
today_formatted <- format(today, format="%B %d %Y")
```

# Fin-spine microchemistry discriminates regional stocks of Caspian Sea starry sturgeon {-}
Shima Bakhshalizadeh^\*a^, Botagoz Murasovna Nasibulina^b^, Tatyana Fedorovna Kurochkin^ab^, Attaala Muhaysin Ali^c^, Theodore W. Hermann^\*d^

^a^Department of Marine Science, Caspian Sea Basin Research Center, University of Guilan, Rasht, Iran. ORCID: 

^b^Faculty of Geology & Geography/Innovative Natural Institute, Astrakhan State University, Shaumyana Str. 1, Astrakhan, Russia

^c^Faculty of Environmental Sciences and Marine Biology, Hadhramout University, Mukalla, Yemen

^d^Institute of Marine Sciences–Fisheries Collaborative Program, University of California, Santa Cruz, Santa Cruz, CA 95064, USA

^\*^**Corresponding authors**:

Dr. Shima Bakhshalizadeh, Department of Marine Science, Caspian Sea Basin Research Center, University of Guilan, Rasht, Iran. Tel: (+98 13) 33691066; Fax: (+98 13) 33691066, E-mail: \href{mailto:sh.bakhshalizadeh@guilan.ac.ir}{sh.bakhshalizadeh@guilan.ac.ir}

Dr. Theodore W. Hermann, Institute of Marine Sciences–Fisheries Collaborative Program, University of California, Santa Cruz, Santa Cruz, CA 95064, USA , E-mail: \href{mailto:thherman@ucsc.edu}{thherman@ucsc.edu}

**ORCIDs**: Shima Bakhshalizadeh: [0000-0002-2683-579X](https://orcid.org/0000-0002-2683-579X), Botagoz Murasovna Nasibulina: [0000-0002-6518-0837](https://orcid.org/0000-0002-6518-0837), Tatyana Fedorovna Kurochkina: [0000-0002-3381-9376](https://orcid.org/0000-0002-3381-9376), Attaala Muhaysin Ali: [0000-0002-8994-6008](https://orcid.org/0000-0002-8994-6008), Theodore W. Hermann: [0000-0003-2632-7338](https://orcid.org/0000-0003-2632-7338)

**Submission date:** `r today_formatted`



\newpage

# Abstract (250 words) {-}

```{r raw-data, echo=FALSE, message=FALSE, include=FALSE}
tar_load(formatted_element_list)
```


```{r fda-res, echo=FALSE, message=FALSE, include=FALSE}

tar_load(fda_accuracy)
tar_load(fda_roc_auc)


```

```{r anova-data, message = FALSE, echo = FALSE, include = FALSE}
# anova_res <- readRDS(here::here("data", "anova_output_data.RDS"))
# tar_load(srh)
# tar_load(sig_elements)
# tar_load(diff_in_sig_elem)
tar_load(sig_elems_formatted)
tar_load(south_higher_formatted)
tar_load(north_higher_formatted)
# sig_reg_res <- srh %>% 
#   dplyr::filter((term == "region") & (p.value < 0.05))

# sig_reg_elems <- sig_reg_res %>% 
#   dplyr::pull(element)

# sig_elems_formatted <- sentence_format_for_list(sig_elements)

# south_higher <- diff_in_sig_elem %>% 
#   dplyr::filter(-delta_from_south < 0) %>% 
#   dplyr::pull(name)

# north_higher <- diff_in_sig_elem %>% 
#   dplyr::filter(delta_from_south > 0) %>% 
#   dplyr::pull(name)

# north_higher_formatted <- sentence_format_for_list(north_higher)
# south_higher_formatted <- sentence_format_for_list(south_higher)

# ba <- anova_res %>% 
#   dplyr::filter(element == "Ba/Ca")
# ba_sex_sig <- ba %>%
#   dplyr::filter(term == "sex") %>% 
#   pull(p.adj) %>% 
#   signif(., digits = 2)

tar_load(dunn_test_res)

male_male_diff <- dunn_test_res %>%
  dplyr::filter(grepl("_male", group1), grepl("_male", group2)) %>%
  dplyr::pull(p.adj) %>%
  signif(., digits = 2)

south_diff <- dunn_test_res %>% 
  dplyr::filter((group2 == "south_male") & (group1 == "south_female")) %>% 
  dplyr::pull(p.adj) %>% 
  signif(., digits = 2)
```

Chemical markers in otoliths have been used to assess the stock structure of many marine fishes, 
but these natural markers have yet to be widely evaluated in the spines of sturgeon fishes in the Caspian Sea, 
which has six endangered sturgeon species. 
We used inductively coupled–plasma mass spectrometry to quantify `r formatted_element_list` in pectoral 
fin spines of starry sturgeon (*Acipenser stellatus*) in the northern and southern Caspian Sea, 
where depth, salinity, and temperature vary from north to south. 
Fin spines showed significant regional differences in 
`r sig_elems_formatted` (Scheirer–Ray–Hare test, p < 0.05). 
Principal component analysis indicated distinct north/south groups when considering all elements in ratio to calcium. 
The centroids of these regional groups differed significantly (PERMANOVA, p < 0.05). 
Flexible discriminant analysis classified `r fda_accuracy`% of fish into their correct regions using all 
element-to-calcium ratios. These results suggest that individuals in different regions share common lifetime
environmental histories and may represent unique stocks in the Caspian Sea. 
Moreover, the findings suggest that pectoral fin-spine microchemistry can be used to identify stocks of starry 
sturgeon, thus providing a non-lethal approach to elucidating life-history details that are critical to the 
comprehensive management of sturgeon resources.

**Keywords**: microchemistry; fin spine; sturgeon; conservation; fisheries; Caspian Sea

\newpage



# Introduction

Anthropogenic activities threaten global fish diversity, especially among large-bodied fishes that rely on freshwater 
for all or part of their life histories [@allan2005; @arthington2016; @he2017; @stone2007]. 
Sturgeons are an ancient group of large anadromous fishes, most of which are listed as threatened or endangered by the 
International Union for Conservation of Nature (IUCN) due to overfishing and loss of 
habitat [@bakhshalizadeh2015; @lukyanenko1999; @pourkazemi2006; @ruban2019]. 
Sturgeons are highly mobile and exploit diverse habitats, which makes it challenging to delineate their 
stocks (i.e., distinct subpopulations) [@beamesderfer1997; @gross2002; @munro2007; @whitmore2018]. 
Moreover, sturgeon spatial distributions can be complex and extensive, varying by sex, life stage, and 
season [@bakhshalizadeh2017; @kahn2019; @whitmore2018a]. A clear understanding of basic life-history details, especially 
movement patterns, is critical for sturgeon conservation and management in the face of numerous 
anthropogenic pressures [@bakhshalizadeh2017; @bakhshalizadeh2012; @pikitch2005; @sulak2002].  



In the Caspian Sea (**Fig. \@ref(fig:map)**), the world’s largest inland body of water, climate change, habitat degradation, 
and fishing pressures threaten important fish stocks, especially those of sturgeons [@barannik2004; @lukyanenko1999; @ruban2019]. 
In many cases, sturgeon migrate through multinational waters, where regulation is not straightforward and fish are exposed to illegal
trawling, purse-seine fisheries and gill-nets [@bakhshalizadeh2017; @friedrich2018; @friedrich2019]. 
Sturgeon conservation and management in the Caspian Sea requires an understanding of migration patterns, site fidelity, and 
connectivity within and among stocks [@bakhshalizadeh2021; @bakhshalizadeh2015; @bakhshalizadeh2011; @mcintyre2015].

```{r label = map, echo = FALSE, warning = FALSE, fig.cap = "The study region, showing neighboring countries, depth profile of the Caspian Sea, and sampling areas (thick red shoreline).", out.width = '100%'}
tar_load(map)
knitr::include_graphics(knitr::plot_crop(map))

```

Quantifying the dispersal of stocks is essential to further our understanding of stock dynamics. 
Tagging and telemetry techniques are valuable for elucidating movement behavior in sturgeons but can be challenging to use in 
the youngest fish classes due to their small body size [@carrera-garcia2017]. 
By contrast, natural tags allow long-term stock-identification studies across individuals of all 
sizes [@allen2009; @arai2002; @campana1999; @chen2019]. 
Calcified structures have been used as sources of natural tags in fisheries science for decades because they incorporate various 
trace and microelements from the ambient environment [@campana1999; @kerr2014; @tzadik2017]. 
Otolith microchemistry is the most widely used tool for studying natural tags because otoliths are metabolically 
inert [@campana1999; @thomas2019] and thus preserve life-long records of environmental exposure. 
However, fish are killed in the process of removing otoliths, which is clearly undesirable when studying threatened species 
such as sturgeons.

Fin rays and spines provide a valuable non-lethal alternative to otoliths for investigating natural tags of 
habitat use [@allen2009; @arai2002; @avigliano2019; @bakhshalizadeh2021a; @cadrin2005; @clarke2007; @kerr2014; @phelps2012; @tzadik2017]. 
The pectoral fin spines of sturgeon originate from cells within the dermis along more than half the anterior edge of the pectoral 
fin and are reinforced with hydroxyapatite (calcium phosphate) and 
collagen [@bakhshalizadeh2019; @bakhshalizadeh2013; @bakhshalizadeh2013a; @loewen2016; @tzadik2017]. 
Like otoliths, sturgeon pectoral spines grow in characteristic bands that can be used to study age and life history of 
individuals [@bakhshalizadeh2011; @pollock2015]. 
Although pectoral spines are not metabolically inert like otoliths, their margins are stable enough to elucidate habitat use and stocks 
based on natural tags [@avigliano2019; @clarke2007; @tzadik2017]. 

Analyzing whole otoliths or fin spines provides microchemistry data integrated across the lifetime of a fish, which can be useful for stock
identification [@campana1999]. 
However, when using whole otoliths or fin spines to identify stocks, age/size composition of the groups being
compared (e.g., fish from different regions) must be carefully considered to minimize microchemical differences due to 
ontogeny rather than, e.g., provenance [@campana2000; @soeth2019]. 
For example, the proportion of fin-spine or otolith microchemistry reflecting adult life history will necessarily increase with fish age,
which could lead to erroneous interpretations of microchemical differences if age differs among sampled groups. 
This is especially important for fin spines, because resorption begins with the innermost material [@tzadik2017], meaning whole fin-spine microchemistry of 
older fish not only includes more adult life-history data than that of younger fish, but also may lack a complete record of early life history.
<!-- 
Sturgeon otoliths are challenging to work with due to their irregular shape and annuli, 
and therefore fin spines have been preferred, including for microchemistry studies [@arai2002].
The Caspian Sea is home to six species of sturgeon, which are overfished and threatened by anthropogenic activities [@pourkazemi2006; @fazli2021].
Although Caspian Sea sturgeon are important commercial fish, many details of their life histories remain unclear.
For example, starry sturgeon (*Acipenser stellatus*) have been traditionally treated as a single stock, although some fish migrate from feeding grounds in 
the southern Caspian Sea to spawn in rivers in the north, while others spawn in southern rivers.
There is no published evidence for homing, but genetic studies have indicated regional differentiation in Caspian Sea sturgeon species, including starry sturgeon
[@pourkazemi1999; @norouzi2016]. -->

Here, we assessed the use of whole pectoral fin-spine microchemistry for discriminating starry sturgeon (*Acipenser stellatus*) from the northern and 
southern Caspian Sea. Previous studies have shown genetic differences in several sturgeon species, including starry sturgeon, between the northern and southern 
Caspian Sea [@pourkazemi1999; @norouzi2016], so we hypothesized that fish sourced from these two regions would similarly show differences in fin-spine microchemistry. 
The successful use of fin spines to discriminate among starry sturgeon from different regions could provide a 
crucial, non-lethal avenue for gathering baseline information about this imperiled fish, which is an important caviar species that 
requires stocking in the Caspian Sea due to overfishing and habitat degradation [@pourkazemi2006; @fazli2021].

\newpage

# Material and Methods

## Study area 

The Caspian Sea has a variable salinity of about 1.2%, roughly one third that of seawater [@matishov2018]. 
It is divided into three distinct basins (north, middle and south) (**Fig. \@ref(fig:map)**). 
The northern basin is by far the shallowest, with a maximum depth of only ~20 m compared with 788 and 1,025 m, respectively, 
for the middle and south basins [@ibrayev2010]. 
The northern basin is also heavily influenced by the input of the Volga River, 
which accounts for about 80% of all river discharge into the Caspian Sea, resulting in a lower salinity [@ibrayev2010; @matishov2018]. 

## Study species 

Starry sturgeon are a large-growing (> 1.7 m) and long-lived (at least 29 years) anadromous 
fish species [@bakhshalizadeh2012; @bakhshalizadeh2017]. 
They spawn in rivers, and the juveniles migrate to shallow coastal waters, where they feed and grow for 3–4 years before 
moving off-shore to mature [@fadeyeva1981]. 
Females move off-shore earlier but mature later than males (maturity at 7 vs. 6 years, respectively) [@bakhshalizadeh2017]. 
Starry sturgeon populations have suffered greatly from environmental degradation and overfishing, 
and are now supported through stocking efforts [@pourkazemi2006; @bakhshalizadeh2021].

## Sample collection, preparation, and analyses 

Adult male (n = `r select_fish("north|south", "male", fish_data)`) and female (n = `r select_fish("north|south", "female", fish_data)`) 
starry sturgeon were collected in the northern and southern Caspian Sea (red shoreline in **Fig. \@ref(fig:map)**; **Table \@ref(tab:fish-table)**) from 
commercial catches harvested with either beach seines (1,000–1,100 m long, 10–15 m deep, and cod-end mesh of 30–33 mm) or gill nets 
(18 m long, 2.1 m deep, and knot-to-knot mesh size of 100 mm). No fish were killed specifically for this project. 
Fish were sexed via macroscopic examination of gonads.

To prepare samples for further analyses, the right marginal pectoral fin (i.e., the most cranial one) was extracted from each fish by cutting it at the articulation point, 
following @koch2008. Removed fin spines were placed in a warm bath of distilled water for 10 min, then cleaned with a brush to remove soft tissues [@bakhshalizadeh2013].
Finally, the samples were air-dried on filter paper and then sonicated for 5 min in ultra-pure water [@bakhshalizadeh2021a].
Fish were aged by counting rings from fin-spine thin-sections under light microscopy [@bakhshalizadeh2012; @bakhshalizadeh2015]. 

Spine samples were analyzed using inductively coupled plasma mass spectrometry 
(ICP-MS; 7500 Series, Agilent, Santa Clara, CA, USA) by the staff at the Aria Sharif Chemical Laboratory (Karaj, Iran). 
Briefly, 6 g samples of cleaned spines were immersed in a 2:1 (v/v) mixture of 65% nitric acid (HNO~3~; Merck, Darmstadt, Germany) and 
60% perchloric acid (HClO~4~; Merck) at 70°C to totally dissolve the spines. 
The obtained solution was then mixed with distilled water in a sampling vial to a volume of 50 mL. 
ICP-MS was used to measure fin spine `r formatted_element_list`. 
A multi-element standard (1094870100SKU; Merck) was used for instrument calibration every five samples. 
The operational conditions for the ICP-MS were optimized following the manufacturer’s instructions, 
as follows: cone, nickel; RF power, 1,500 W; nebulizer gas flow rate, 0.6 L/min; plasma gas flow rate, 12 L/min; auxiliary gas flow rate, 
1 L/min; and integration time, 6 s.

```{r, echo = FALSE}
tar_load(length_u_test_res)
tar_load(age_u_test_res)
tar_load(sex_prop_test)
tar_load(region_age_summary)
tar_load(region_length_summary)

south_length <- region_length_summary %>% .[region == "south", median]
south_length_mad <- region_length_summary %>% .[region == "south", mad] %>% signif(3)
north_length <- region_length_summary %>% .[region == "north", median]
north_length_mad <- region_length_summary %>% .[region == "north", mad]%>% signif(3)

south_age <- region_age_summary %>% .[region == "south", median]
south_age_mad <- region_age_summary %>% .[region == "south", mad]%>% signif(3)
north_age <- region_age_summary %>% .[region == "north", median]
north_age_mad <- region_age_summary %>% .[region == "north", mad]%>% signif(3)

south_length_formatted <- plus_minus(south_length, south_length_mad)
north_length_formatted <- plus_minus(north_length, north_length_mad)
south_age_formatted <- plus_minus(south_age, south_age_mad)
north_age_formatted <- plus_minus(north_age, north_age_mad)

south_males <- select_fish("south", "male", fish_data)
south_females <- select_fish("south", "female", fish_data)
north_males <- select_fish("north", "male", fish_data)
north_females <- select_fish("north", "female", fish_data)

south_ratio <- glue::glue("{south_males}/{south_females}")
north_ratio <- glue::glue("{north_males}/{north_females}")

```

## Data analyses

We found no significant differences in age (median ± M.A.D.: south, `r south_age_formatted` years vs. north, `r north_age_formatted` years;
Mann–Whitney U test, `r in_text_pval(age_u_test_res$p)`), 
total length (south, `r south_length_formatted` cm vs. north, `r north_length_formatted` cm; Mann–Whitney U test, `r in_text_pval(length_u_test_res$p)`), 
and sex ratio (males/females: south, `r south_ratio` vs. north, `r north_ratio`; 
two-sided proportion test, `r in_text_pval(sex_prop_test$p_value)`)
between regions, indicating that our samples were sufficiently comparable to minimize differences in microchemistry due to ontogeny rather than
environmental history [@campana2000]. Elemental contents were normalized relative to Ca. 
<!-- Sr/Ba was also evaluated, given its high sensitivity to transitional estuarine environments [@mcculloch2005; @walther2011].  -->
All data were examined for normality and homogeneity before performing statistical analyses [@quinn2002].
Some elemental ratios failed the assumption of normality (both transformed and log-transformed) for two-way analysis of variance (ANOVA).
Therefore, we used a non-parametric alternative, the Scheirer–Ray–Hare (SRH) extension of the Kruskal–Wallis test, to evaluate the effects of sex, region, 
and the interaction thereof on element-to-calcium ratios [@sokal1995; @scheirer1976]. 
Dunn's test for multiple comparisons was performed in the case of any significant interactions [@dunn1964].

Principal component analysis (PCA) and permutational ANOVA (PERMANOVA) were used to investigate 
regional differences across all significant elemental ratios [@soeth2019; @schroeder2022; @oksanen2022]. 
PERMANOVA was performed with Euclidean distance and 10,000 permutations using the `adonis2` function in the 
R package `vegan` [@oksanen2022]. 
Flexible discriminant analysis (FDA) was used to estimate the percentage of fish that could be correctly 
classified into their regions based on their whole fin-spine microchemistry [@friedman2018]. FDA performance was evaluated using four-fold 
cross-validation. That is, the data were divided into four unique subsets stratified by region. Then, three of the four subsets were used
to build the model, while the remaining one was used to evaluate model performance. This process was repeated for all subsets. 
To reduce the influence of random subsetting on model performance, the whole process was repeated 1,000 times. Model performance metrics
(accuracy and receiver opeating curve [ROC] area under the curve [AUC]) were averaged across all models.
FDA was performed using the `tidymodels` and `discrim` packages in R [@tidymodels; @discrim]. 
All analyses not otherwise listed were performed in R [@R]. 
Visualizations were created using `ggplot2` in R [@ggplot2]. 
Map data in **Fig. \@ref(fig:map)** were sourced from Natural Earth [@natearth] and GEBCO [@gebco].



```{r fish-table, echo=FALSE}
tar_load(fish_table)
kable(fish_table, format = "pandoc", caption = "Summary statistics for starry sturgeon (*Acipenser stellatus*) collected from the northern and southern Caspian Sea. Sampling areas correspond to the red highlighted coastlines in **Fig. 1**. Total length is the median value. M.A.D., median absolute deviation.")
```


\newpage

# Results 

```{r fish-data, message = FALSE, echo = FALSE, include = FALSE}

tar_load(fish_data)
tar_load(total_fish)
```

Fin spines from a total of `r total_fish` fish were sampled (`r south_males` males and
 `r south_females` females from the south; `r north_males` males 
 and `r north_females` females from the north) (**Table \@ref(tab:fish-table)**). 
 `r sig_elems_formatted` in pectoral fin spines of starry sturgeons differed significantly 
 (Scheirer–Ray–Hare test, p < 0.05) between geographic regions (**Fig. \@ref(fig:bar-chart)**, **Table \@ref(tab:anova-table)**); 
 fish from the southern Caspian Sea had significantly lower `r north_higher_formatted`, but higher `r south_higher_formatted`, 
 than fish from the northern Caspian Sea. No elements differed significantly by sex. Ba/Ca was the only element whose interaction term was significant.
 Dunn's test inidicated this was due to significant differences between northern and southern 
 males (adjusted p = `r male_male_diff`) and between southern males and southern females 
 (adjusted p = `r south_diff`).


```{r label = bar-chart, echo = FALSE, warning = FALSE, fig.cap = "Median element-to-calcium ratios in pectoral spines of starry sturgeon from the northern and southern Caspian Sea. Error bars show median absolute deviation. P-values indicate significant differences based on the Scheirer–Ray–Hare extension of the Kruskal–Wallis test."}

tar_load(srh_bar_chart)
knitr::include_graphics(knitr::plot_crop(srh_bar_chart))
# knitr::include_graphics(here(srh_bar_chart))

```


\newpage
```{r anova-table, echo=FALSE, message=FALSE}
tar_load(formatted_srh_table)

kable(
  formatted_srh_table, 
  format = "pandoc", 
  # align = "c", 
  longtable = T, 
  caption = "Results of the Scheirer–Ray–Hare extension of the Kruskal–Wallis test. Element-to-calcium ratios in male and female starry sturgeon from the northern and southern Caspian Sea were compared. '*' indicates significance at p < 0.05.",
  booktabs = T, 
  digits = 3, 
  font_size = 7
  ) 

```

\newpage

```{r pca-prep, echo=FALSE, message=FALSE, include=FALSE}
tar_load(pc_vars)

```
\newpage


PCA was conducted using the elemental ratios that showed significant differences between fish from the northern and 
southern Caspian Sea in ANOVA (i.e., `r sig_elems_formatted`). 
The first four principal components accounted for `r sum(pc_vars)`% of the total variation 
(PC1 = `r pc_vars[1]`%, PC2 = `r pc_vars[2]`%, PC3 = `r pc_vars[3]`%, and PC4 = `r pc_vars[4]`%) (**Fig. \@ref(fig:pca)**). 
PERMANOVA of the distance matrix of the principal components showed significant differences for region 
(p < 0.05, **Table \@ref(tab:adonis)**). Cross-validated classification by FDA yielded an accuracy 
of `r fda_accuracy`% and an ROC AUC value of `r fda_roc_auc` when classifying
fish into regions based on spine microchemistry.



```{r adonis, echo=FALSE}
# adonis_tab <- readRDS(here::here("figures", "adonis.RDS"))
tar_load(adonis_table)


kable(adonis_table, digits = 2, format = "pandoc", align = "c", caption = "Permutational analysis of variance (PERMANOVA) results for the distance matrix of principal components of significant element-to-calcium ratios.")
```


\newpage

```{r label = pca, echo = FALSE, warning = FALSE, fig.cap = "A) Principal component analysis (PCA) score plot of trace element-to-calcium ratios in pectoral spines of starry sturgeon from the northern (blue circles) and southern (red triangles) Caspian Sea. Ellipses are for visual aid only. Squares indicate data centroids. B) Absolute values of contributions from elemental ratios to PCs. Dots indicate negative values, while slashes indicate positive values.", out.width = '100%'}

tar_load(full_pca_fig)

knitr::include_graphics(knitr::plot_crop(full_pca_fig))

```


\newpage

# Discussion

Our analyses of starry sturgeon pectoral fin spines revealed significant variation in `r sig_elems_formatted` 
between fish from the northern and southern Caspian Sea.
Multivariate analyses using all elemental ratios indicated distinct regional groups.
Furthermore, classification success to geographic regions using elemental variation was high (`r fda_accuracy`%). 
These results show that starry sturgeon in the northern and southern Caspian Sea differed in the environments to which they 
were exposed over the course of their lifetime, suggesting that fish in these regions may represent different stocks.

<!-- Detailed life-history parameters are not known for the starry sturgeon examined in this study. 
However, microelements reflecting both environmental and biological factors differed in fin spines from fish 
collected in different regions, suggesting that fish from the northern and southern Caspian Sea may differ across a 
suite of life-history factors, such as habitat exploitation, growth, and/or feeding.  -->
The geography of the basin likely plays a large role in the observed chemical differences. 
The northern basin is extremely shallow and influenced by the freshwater discharge of the Volga River [@ibrayev2010; @matishov2018], 
resulting in a large, open, estuarine basin with lower salinity (**Fig. \@ref(fig:map)**).
By contrast, the south is characterized by a relatively narrow band of shallow coastal water surrounding a large, deep basin.
Thus fish in the north are exposed to higher riverine inputs and much lower salinity [@tuzhilkin2005].
This is consistent with the results of the present study, which showed lower `r south_higher_formatted` and higher `r north_higher_formatted` in
fish from the north [**Fig. \@ref(fig:bar-chart)**].
Although the pathways governing fin-spine microchemistry remain unknown [@loewen2016],
recent studies have begun to reveal the complex mechanisms underlying those of otoliths [@hussy2020; @thomas2019a; @thomas2017; @thomas2019], 
which are likely similar given the correlation between otolith and fin-spine microchemistry [@gillanders2001; @tzadik2017].

Sr in calcified structures has a relatively long history of use in elucidating fish
life histories [@campana1999; @elsdon2008; @hussy2020]. Sr/Ca in calcified parts of fish is 
strongly correlated with water chemistry [@hussy2020; @walther2006] and is useful for indicating transitions from freshwater 
to estuarine or marine water and vice versa [@hermann2016; @mcculloch2005; @tabouret2010; @walther2011].
The lower Sr/Ca we observed in fin spines of northern starry sturgeon is consistent with the lower salinity of this region, indicating
fish from different regions likely had different lifetime salinity exposure.
B/Ca was also lower in fish from the north.
Boron correlates positively with salinity in seawater [@kulinski2017], and B/Ca
in calcified organisms such as foramenifera correlates positively with pH [@yu2007]. Recent studies in otoliths have suggested similar relationships,
although the literature is still sparse and the results somewhat mixed [@limburg2023; @cavole2023]. A similar association between salinity/pH may exist
with B/Ca in fin spines, which would be consistent with our results.

In otoliths, both Zn and Cu likely reflect feeding and/or growth processes due to their physiological roles, rather than directly reflecting ambient water chemistry
[@hussy2020; @thomas2017; @ranaldi2008]. Elevated otolith Zn/Ca and Cu/Ca has been associated with anthropogenic effects [@arslan2005], suggesting these elements
may reflect pollutants from the environment obtained via prey items. @heidary2012 reported bioaccumulation of Zn and Cu in the tissues of starry sturgeon,
while @bakhshalizadeh2023 found significantly higher heavy metals in fin spines of starry sturgeon from the north vs. those from the south.
Exposure to pollutants may be higher in the north Caspian Sea due to the strong influence of the
Volga and Ural rivers, thus explaining the elevated Zn/Ca and Cu/Ca observed in fin spines of northern starry sturgeon.
Mn concentration has been associated with anthropogenic influences on river inputs as well as
estuarine processes in rivers during low flow [@schroeder2022; @nelson2020]. 
Mn/Ca in otoliths has also been used as a proxy for hypoxic conditions [@limburg2011; @limburg2015], which can occur when stratification occurs in estuaries
[@schroeder1999; @nelson2020].
During the summer months, large areas of bottom water in the north Caspian Sea can have hypoxic conditions depending on annual flow conditions [@tuzhilkin2005].
Therefore, the significant differences in fin-spine Mn/Ca observed here may have been due to the the heavy influence that river 
flow has on the physico-chemical conditions in the north basin [@tuzhilkin2005].
There is little literature investigating pathways by which Si enters calcified structures of fish. However, Si/Ca is used as a proxy for terrestial sediment runoff in
biochemical and paleoenvironmental studies [e.g., @bunzel2017]. This is consistent with our observations that Si/Ca was higher in fin spines of
north Capsian Sea fish, but futher study is required.

Finally, Ba/Ca was the only elemental ratio that showed significant differences for the interaction between region and sex. Males in the south had significantly
different values than males in the north and females in the south.
Ba/Ca in calcified parts of fish is strongly correlated with water chemistry [@hussy2020; @walther2006] and useful for indicating transitions from freshwater 
to marine water and vice versa [@hermann2016; @mcculloch2005; @tabouret2010; @walther2011].
Therefore, our results may reflect the earlier off-shore movements of females compared to males in the south [@bakhshalizadeh2017]. 
Such differences may not have been observed in northern fish due to the similarities in near-shore and off-shore 
environments (i.e., relatively uniform, shallow depth across the northern basin; **Fig. \@ref(fig:map)**).
These results should be approached with caution, however.
The south Caspian Sea has considerable environmental variability [@fallah2022] and Ba can derive from numerous sources [@correia2021]. 
Furthermore, differences in Ba/Ca have been observed between starry sturgeon from the eastern and western
parts of the south Caspian Sea [@bakhshalizadeh2021a].
Given our small sample size and uneven sampling between the southeastern and southwestern Caspian Sea (**Table \@ref(tab:fish-table)**),
it is uncertain whether this result was due to within-region variation in environmental Ba or fish behavior, 
or would disappear entirely with a larger sample size.


<!-- Boron correlates positively with salinity in seawater [@kulinski2017], and B/Ca
in calcified organisms such as foramenifera correlates positively with pH [@yu2007]. Recent studies in otoliths have suggested similar relationships,
although the literature is still sparse and the results somewhat mixed [@limburg2023; @cavole2023]. Given the correlation between otolith and 
fin-spine microchemistry [@gillanders2001; @tzadik2017], it would not be unreasonable to hypothesize that such a relationship exists for fin-spine microchemistry as well. This would be
consistent with the lower B/Ca observed in sturgeon from the northern Caspian Sea, as fish in the north likely are likely exposed to lower salinity over their lifetime.
 This may explain higher levels of these rations in fin spines of northern fish, 
which are exposed to more freshwater discharge than fish from the south.  -->

<!-- Feeding strategies may also differ somewhat between fish from the north and south.
Juvenile sturgeon spend the first 
Interestingly, male starry sturgeon in the southern Caspian Sea had significantly lower Ba/Ca than females. 
This may reflect the earlier off-shore movements of females compared to males [@bakhshalizadeh2017]. 
Such differences may not have been observed in northern fish due to the similarities in near-shore and off-shore 
environments (i.e., relatively uniform, shallow depth across the northern basin; **Fig. \@ref(fig:map)**), 
although this hypothesis needs to be tested with water samples and additional fish. -->

Stocking may have also influenced the observed results. 
Caspian Sea sturgeon stocks have been devastated by fishing and environmental degradation, and all six species present are 
supported by artificial stocking efforts [@pourkazemi2006]. 
Fish stocked in Russia in the north, for example, may differ genetically, behaviorally, physiologically, etc., 
from those stocked in Iran in the south, in addition to being exposed to different environments. 
For example, differences in maturation and growth rates have been observed between northern and southern starry sturgeon [@khodorevskaya2014].
This could have influenced the observed significant regional differences in Mn/Ca, Zn/Ca, and Cu/Ca, as all of these
ratios in otoliths have been associated with growth processes [@hussy2020; @thomas2017].
Fin-spine microchemistry has been shown to vary significantly among age-0 sturgeon from different hatcheries in 
Iran [@bakhshalizadeh2021a], so it would not be unreasonable that even starker differences exist between fish stocked by 
different national authorities. 
This could be further complicated by differences in survivorship of stocked vs. naturally spawned fish and/or 
stocking rates in the north and south, especially given the environmental differences between regions. 
Although hatchery water may have influenced the elemental ratios observed in the present study to some degree, 
fin spine resorption occurs from the innermost material outwards [@tzadik2017]. 
Thus, the influence of hatchery water chemistry on the lifetime fin-spine microchemistry of adult fish should be non-existent to minimal.

<!-- Although the pathways governing fin-spine microchemistry remain unknown [@loewen2016], 
recent studies have begun to reveal the complex mechanisms underlying those of otoliths [@hussy2020; @thomas2019a; @thomas2017; @thomas2019], 
which are likely similar. 
Sr and Ba in calcified structures have a relatively long history of use in elucidating fish 
life histories [@campana1999; @elsdon2008; @hussy2020]. The ratios of these elements to calcium in calcified parts of fish are 
strongly correlated with water chemistry [@hussy2020; @walther2006] and are useful for indicating transitions from freshwater 
to marine water and vice versa [@hermann2016; @mcculloch2005; @tabouret2010; @walther2011]. 
Zn and Cu in calcified structures appear to be de-coupled from concentrations in ambient water [@hussy2020; @thomas2017]. 
In otoliths, they may play a physiological role as co-factors for enzymes associated with the otolith protein matrix [@thomas2017] 
and may therefore be indicative of fish physiology. Mn likely reflects both environmental concentrations and fish 
physiology [@hussy2020; @limburg2018]. 
The pathways by which B and Si enter calcified structures of fish remain poorly studied. 
Therefore, the microchemical differences observed here likely represent a complex mix of differences in lifetime 
environmental history, genetics, physiology, and behavior. -->

Our study had some limitations that future studies can address.
First, our sample size was small. 
Acquiring samples of these rare fish is challenging, but a larger sample size
would have allowed us to be more selective of the fish included (e.g., to reduce the variability in fish age) and
improve the detection of meaningful significant results vs. those that happened by chance (as may have been the case with Ba/Ca).
Second, we used whole fin spines rather than analyzing transects of cross-sections (e.g., via laser ablation ICP-MS).
A transect approach would have provided finer-scale environmental data that could be correlated to growth rings and thus specific life-history changes
[@campana1999; @elsdon2008]. Transect data also would have allowed us to compare fish of disparate ages, as the relationship between microchemical data
and age is not obscured by integrating over the lifetime of the fish.

We found that whole fin-spine microchemistry was effective at discriminating starry sturgeon 
from different regions in the Caspian Sea. 
Elemental data suggest that starry sturgeons may have different life 
histories in the northern and southern Caspian Sea and therefore could represent different stocks. 
These results provide baseline information required for the conservation and management of these imperiled and poorly understood fish. 
Our study also adds to a growing body of literature demonstrating that fin-spine microchemistry is a valuable, 
non-lethal tool for assessing the life histories of threatened fish 
species [@allen2009; @arai2002; @avigliano2019; @bakhshalizadeh2021a; @cadrin2005; @clarke2007; @kerr2014; @phelps2012; @tzadik2017]. 
Microchemistry allows scientists and managers to rapidly gather life-history data from relatively small sample sizes. 
However, as in other threatened and poorly understood systems, additional efforts are needed to realize the potential of this method 
as a conservation tool [@hermann2021]. 
The regional diversity in sturgeon fin-spine microchemistry demonstrated here requires further study and could be cause 
for management action. 
This includes studies of the environment–fin spine pathways mediating the uptake of elements; 
international research and management cooperation (especially given the transboundary migrations that sturgeons can undertake); 
and fin-spine microchemical studies that include all Caspian Sea sturgeon species. 
A broad, long-term, and international investigation of sturgeon fin-spine microchemistry in the Caspian Sea could provide a 
research and management framework for other poorly studied regions with threatened species.

\newpage

# Declaration of Competing Interests {-}

The authors declare that they have no conflict of interest.

# Acknowledgements {-}

This research was supported by the University of Guilan, Iran (reference grant no. 15p-90496-1398.7.13), and Astrakhan State University, Russia (reference grant no. 15p-108655-1399.9.29). We would like to thank Guilan University sectors including Security, Vice-Chancellor Research, and Director of International Scientific Cooperation Office, as well as the Iranian Port and Marine Administration and Caspian Sea Shipping Line for their assistance.

# CRediT authorship contribution statement {-}

Shima Bakhshalizadeh: conceptualization, sample collection and preparation, data evaluation, statistical analysis, writing - original draft, writing - review & editing, visualization, funding acquisition.  

Botagoz Murasovna Nasibulina: conceptualization, sample collection and preparation, funding acquisition, writing - original draft  

Tatyana Fedorovna Kurochkina: sample collection and preparation, visualization, writing - review & editing.  

Attala Muhaysin Ali: conceptualization, writing - original draft, writing - review & editing.  

Theodore Hermann: conceptualization, statistical analysis, writing - original draft, writing - review & editing, visualization.

\newpage

# References {-}

<div id="refs"></div>

<!-- # ```{r icpms, echo=FALSE, message=FALSE} -->
<!-- # icpms_pars <- read_csv(here::here("data", "icpms_params.csv")) -->
<!-- # kable(icpms_pars, format = "pandoc", caption = "Operational parameters for the inductively coupled plasma mass spectrometer.") -->
<!-- # ``` -->



